%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[11pt,a4paper, sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[scale=0.86]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\firstname{Biao} % Your first name
\familyname{Jia} % Your last name
% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{University of North Carolina at Chapel Hill}{Chapel Hill, NC}
\mobile{(+1)919-564-8866}
\email{biao@cs.unc.com}
\homepage{github.rmqlife.io}{}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/head-2} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%----------------------------------------------------------------------------------------
\begin{document}
\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\cventry{Aug.2016-Present}{University of North Carolina at Chapel Hill}{ph.D candidate}{Computer Science Department}{advised by Dinesh Manocha}{}{}
\cventry{Sept.2010-July.2014}{Tsinghua University}{Beijing}{B.Eng} {Computer Science and Technology}{}{} 
% Arguments not required can be left empty
\section{Relevant Skills}
\cvitem{Language}{C++, Python, Matlab, Bash, Java}
\cvitem{Framework}{ROS, OpenCV, OpenAI, Flask, tessaract, NLTK}
\section{Employment History}
\cventry{Jan.2017}{University of North Carolina at Chapel Hill}{Teaching Assitant}{}{}{
\begin{itemize}
\item{Comp 410.1 Data Structure}
\end{itemize}
}

\cventry{July.2014-May.2015}{Landscape Mobile Tech Co.,Ltd.}{Beijing}{Algorithm Engineer}{}{
Designed algorithm for two iOS apps: Sight and Screenshots.  
\begin{itemize}
\item{Built an iOS application dataset and a application classifier with interns.}
\item{Enhanced the OCR rate on screenshots of tesseract by rebuilding models and rewriting functions.}
\item{Designed an algorithm to grab the icons and pictures on the screenshots.}
\end{itemize}
}
\section{Research Experience}
\cventry{Aug. 2016}{Resolution-Complete Multi-agent Motion Planning with Arbitrarily-Shaped Obstacles}{submitted to AAAI 2017}{coauthor with Liang He, Dinesh Manocha}{}
{
We highlight its performance on challenging 2D benchmarks and highlight the benefits over prior methods.
}
\cventry{Spring.2014}{Pedestrian Segmentation after Detection}{Diploma Project}{advised by Ai Haizhou}{}
{
Apply superpixel segmentation, probabilistic model and sparse codinng to compute the segmentation confidence map. Highlight in computing efficiency.
}
\cventry{Summer.2013}{Context based Binary Image Retrieval  based on Visual Vocabulary}{Hong Kong Polytechnic University}{submitted to ICPR 2014}{}
{
Application of this algorithm is to patent image retrieval.
}

\section{Courses}
\cventry{Graduate}{University of North Carolina at Chapel Hill}{}{}{}{
\begin{itemize}
\item{Motion Planning}
\item{3D Computer Vision}
\item{Advanced Machine Learning}
\item{Natural Language Processing}
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%-------------------------------------------------------------------------------------
\section{Awards}
\cventry{Sep. 2011}{Scholarship in Tsinghua University }{3rd Place}{}{}{}
\cventry{Nov. 2008}{National Olympiad in Informatics in Provinces}{1st Prize}{}{}{}
\cventry{Nov. 2007}{National Olympiad in Informatics in Provinces}{1st Prize}{}{}{}

\end{document}
